Associations between Chlorophyll \emph{a} and various Microcystin-LR Health Advisory Concentrations

### 2015-12-04 manuscript/manuscript.tex
closes #5 plus some changes to discussion and abstract from addition of thresholds table.

Cyanobacteria harmful algal blooms (cHABs) are associated with a wide
range of adverse health effects that stem mostly from the presence of
cyanotoxins. To help protect against these impacts, several health
advisory levels have been set for some toxins. In particular, one of the
more common toxins, microcystin, has several advisory levels set for
drinking water and recreational use. However, compared to other water
quality measures, field measurements of microcystin are not commonly
available due to cost and advanced understanding required to interpret
results. Addressing these issues will take time and resources. Thus,
there is utility in finding indicators of microcystin that are already
widely available, can be estimated quickly and \emph{in situ}, and used
as a first defense against high levels of microcystin. In particular,
chlorophyll \emph{a} is very commonly measured, can be estimated
\emph{in situ}, and has been shown to be positively associated with
microcystin. In this paper, we use this association to provide estimates
of chlorophyll \emph{a} concentrations that if exceeded would be
indicative of a higher probability of exceeding select health advisory
concentrations for microcystin-LR. Using the 2007 National Lakes
Assessment and a conditional probability approach, we identify
chlorophyll \emph{a} concentrations that are more likely than not to be
associated with an exceedance of a microcystin health advisory level. We
look at the recent US EPA health advisories for drinking water as well
as the World Health Organization levels for drinking water and
recreational use. For the specific advisory microcystin concentrations
of 0.3, 1, 1.6, and 2, we find chlorophyll \emph{a} concentrations of
0.07, 0.07, 2.79, and 11.36, respectively. When managing for these
various microcystin levels, exceeding these reported chlorophyll
\emph{a} concentrations should be a trigger for further testing and
possible management action.

@@

Over the last decade or so numerous events and legislative activities
have raised the public awareness of harmful algal blooms (Rinta-Kanto et
al. 2009, HABHRCA 2014, Jetoo et al. 2015), and in response the US
Environmental Protection Agency (USEPA) has recently released suggested
microcystin-LR (one of the more common toxins) concentrations that would
trigger health advisories (McElhiney and Lawton 2005, Zurawell et al.
2005, USEPA 2015). Additionally, the World Health Organization (WHO) has
had proposed advisory levels for drinking water and a range of
recreational risk levels (Chorus and Bartram 1999, Organization 2003).
While these levels and associated advisories are likely to help mitigate
the impacts from harmful algal blooms, they are not without
complications.

One of these complications is that they rely on available measurements
of microcystin-LR. While laboratory testing remains the gold standard
for quantifying microcystin-LR concentrations in water samples, several
field test kits have been developed. Even though field tests provide a
much needed means for rapid assessment, they are not yet widely used and
are moderately expensive (approximately \$150-\$200 depending on
specific kit) with a limited shelf life (typically one year) (James et
al. 2011, Aranda-Rodriguez et al. 2015). Additionally, each technique
requires nuanced understanding of the detection method (e.g., limit of
detection, specific microcystin variants being measured, and sampling
protocol).

@@

We used the 2007 NLA water quality and microcystin-LR concentration data
(USEPA 2009). These data represent a snapshot of water quality from the
summer of 2007 for the conterminous United States. Data on chlorophyll
\emph{a} and microcystin-LR concentrations are available for lakes.

@@

Conditional probability analysis provides information about the
probability of observing one event given another event has also occured.
For this analysis, we used CPA to examine how the conditional
probability of exceeding one of the health advisories changes as
chlorophyll \emph{a} increases in a lake. We expect to find higher
chlorohpyll \emph{a} concentrations to be associated with higher
probabilities of exceeding the microcystin-LR health advisory levels. We
also caclulated bootstrapped 95\% confidence intervals (CI) using 1000
bootstrapped samples. Thus, to identify chlorophyll \emph{a}
concentrations of concern we identfiy the value of the upper 95\% CI
across a range of conditional probabilities of exceeding each health
advisory level. As both microcystin-LR and chlorophyll \emph{a} values
were highely skewed right, a log base 10 transformation was used.
Additional details of the specific implementation are available at
\url{https://github.com/USEPA/microcystinchla}. A more detailed
discussion of CPA is beyond the scope of this paper, but see Paul et al.
(2005) and Hollister et al. (2008) for greater detail.

@@

In the 2007 NLA, microcystin-LR concentrations ranged from 0.05 to 225
\(\mu\)g/L. Microcystin-LR concentrations of 0.05 \(\mu\)g/L represent
the detection limits. Any value greater than that indicates the presence
of microcystin-LR. Of those lakes with microcystin, the median
concentration was 0.51 and the mean was 3.17. Of all lakes sampled, 21\%
of lakes exceeded the USEPA Child level, 8.8\% of lakes exceeded the
USEPA Adult level,11.7\% of lakes exceeded the WHO Drinking level,and
7.3\% of lakes exceeded the WHO Recreational level. For chlorophyll
\emph{a}, the range was 0.07 to 936 \(\mu\)g/L. All lakes had reported
chlorophyll \emph{a} concentrations that exceeded detection limits. The
median concentration was 7.79 \(\mu\)g/L and the mean was 29.63
\(\mu\)g/L. The associations between chlorophyll \emph{a} and the upper
confidence interval across a range of conditional probability values is
shown in Table \ref{tab:mc_chla_table}. Specific chlorophyll \emph{a}
that are associated with greater than even odds of exceeding the
advisory levels were 0.07, 0.07, 2.79, and 11.36 for 0.3, 1.0, 1.6 and
2.0 \(\mu\)g/L advisory levels, respectively (Table
\ref{tab:mc_chla_table} \& Figure \ref{fig:multi_cp_plot}).

@@

The association between Log10 microcystin-LR and Log10 chlorophyll
\emph{a} shows a wedge pattern (Figure \ref{fig:chla_micro_scatter}).
This indicates that higher concentrations of microcystin-LR almost
always co-occur with higher concentrations of chlorophyll \emph{a} yet
the inverse is not true. Higher chlorophyll \emph{a} is not necessarily
predictive of higher microcystin-LR concentrations; however, chlorophyll
\emph{a} may be predictive of the probability of exceeding a certain
concentration.

This is the case as the probability of exceeding each of the four tested
health advisory levels increases as a function of chlorophyll \emph{a}
concentration (Figure \ref{fig:multi_cp_plot}). We use this association
to identify chlorophyll \emph{a} concentrations that are associated with
greater than even odds of exceeding a given health advisory level (Table
\ref{tab:mc_chla_table}). These represent 99.9\%, 99.9\%, 77\%, and
43.8\% of sample lakes for the USEPA Child, the WHO Drinking, the USEPA
Adult, and the WHO recreational levels, respecitvely.

Furthermore, the chlorophyll \emph{a} cutoffs may be used to predict
whether or not a lake exceeds the microcystin-LR health advisories.
Doing so allows us to compare the accuracy of the prediction as well as
evaluate false negatives. Total accuracy of the four cutoffs predicting
microcystin-LR exceedances were 21\% for the USEPA children's advisory,
12\% for the WHO drinking water advisory, 31\% for the USEPA adult
advisory and, 61\% for the WHO regreational advisory (Tables
\ref{tab:child_conmat_table}, \ref{tab:who_drink_conmat_table},
\ref{tab:adult_conmat_table}, \& \ref{tab:who_rec_conmat_table}).
However, total accuracy is only one part of the prediction performace
with which we are concerned.

When using the chlorophyll \emph{a} cutoffs as an indicator of
microcystin-LR exceedances, the error that should be avoided is
predicting that no exceedance has occurred when in fact it has. In other
words, we would like to avoid Type II errors and minimize the proportion
of false negatives. For the four chlorophyll \emph{a} cut-offs we had a
proportion of false negatives of 0\%, 0\%, 0\% and , 1\% for the U.S EPA
childrens drinking water, the WHO drinking water, the USEPA adult
drinking water, and the WHO recreational advisories, respectively. In
each case we miss less than 10\% of the lakes that are in fact exceeding
the microcystin-LR advisory.

@@

A second potential use is to identify possible bloom events from
historical data. As harmful algal blooms are made up of many species and
have various mechanisms responsible for adverse impacts (e.g.~toxins,
hypoxia, odors), there is no single definition of a bloom. For cHABs one
approach has been to identify an increase over a baseline concentration
of phycocyanin (Miller et al. 2013). This is a useful approach for
targeted studies, but phycocyanin is also not always available and
measures the predominance of cyanobacterial pigments and not toxins.
Using our chlorophyll \emph{a} cutoffs provides a value that is more
directly associated with microcystin-LR and can be used to classify
lakes, from past surveys, as having bloomed.

Lastly, using chlorophyll \emph{a} is not meant as a replacement for
testing of microcystin-LR. It should be used when other, direct
measurements of cyanotoxins are not available. In those cases, which are
likely to be common at least in the near future, using a more ubiquitous
measurement, such as chlorophyll \emph{a} will provide a reasonable
proxy for the probability of exceeding a microcystin-LR health advisory
level and provide better protection against adverse effects in both
drinking and recreational use cases.

@@

\begin{longtable}[c]{@{}rrrrr@{}}
\caption{Chlorophyll \textit{a} concentrations that are associated with
a 50\% probability of exceeding a microcystin-LR health advisory
concentration. \label{tab:mc_chla_table}}\tabularnewline
\toprule
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO
Recreational\tabularnewline
\midrule
\endfirsthead
\toprule
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO
Recreational\tabularnewline
\midrule
\endhead
0.1 & 0.07 & 0.07 & 0.07 & 1.47\tabularnewline
0.2 & 0.07 & 4.42 & 11.47 & 19.04\tabularnewline
0.3 & 2.79 & 16.32 & 30.62 & 52.70\tabularnewline
0.4 & 11.36 & 38.30 & 69.19 & 82.22\tabularnewline
0.5 & 23.68 & 65.20 & 84.96 & 103.90\tabularnewline
0.6 & 38.30 & 98.46 & 136.66 & 125.40\tabularnewline
0.7 & 68.85 & 133.20 & 871.20 & 871.20\tabularnewline
0.8 & 114.62 & 338.40 & 871.20 & 871.20\tabularnewline
0.9 & 198.72 & 516.00 & 871.20 & 871.20\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the USEPA
childrens drinking water advisory.
\label{tab:child_conmat_table}}\tabularnewline
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endfirsthead
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endhead
FALSE & 1 & 0\tabularnewline
TRUE & 810 & 217\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the WHO
drinking water advisory.
\label{tab:who_drink_conmat_table}}\tabularnewline
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endfirsthead
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endhead
FALSE & 1 & 0\tabularnewline
TRUE & 906 & 121\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the USEPA adult
drinking water advisory. \label{tab:adult_conmat_table}}\tabularnewline
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endfirsthead
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endhead
FALSE & 234 & 4\tabularnewline
TRUE & 703 & 87\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the WHO
recreational water advisory.
\label{tab:who_rec_conmat_table}}\tabularnewline
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endfirsthead
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endhead
FALSE & 566 & 15\tabularnewline
TRUE & 387 & 60\tabularnewline
\bottomrule
\end{longtable}

>>>>

Cyanobacteria harmful algal blooms (cHABs) are associated with a wide
range of adverse health effects that stem mostly from the presence of
cyanotoxins. To help protect against these impacts, several health
advisory levels have been set for some toxins. In particular, one of the
more common toxins, microcystin, has several advisory levels set for
drinking water and recreational use. However, compared to other water
quality measures, field measurements of microcystin are not commonly
available due to cost and advanced understanding required to interpret
results. Addressing these issues will take time and resources. Thus,
there is utility in finding indicators of microcystin that are already
widely available, can be estimated quickly and \emph{in situ}, and used
as a first defense against high levels of microcystin. Chlorophyll
\emph{a} is commonly measured, can be estimated \emph{in situ}, and has
been shown to be positively associated with microcystin. In this paper,
we use this association to provide estimates of chlorophyll \emph{a}
concentrations that are indicative of a higher probability of exceeding
select health advisory concentrations for microcystin-LR. Using the 2007
National Lakes Assessment and a conditional probability approach, we
identify chlorophyll \emph{a} concentrations that are more likely than
not to be associated with an exceedance of a microcystin health advisory
level. We look at the recent US EPA health advisories for drinking water
as well as the World Health Organization levels for drinking water and
recreational use and identify a range of chlorophyll \emph{a}
thresholds. A 50\% chance of exceeding one of the specific advisory
microcystin concentrations of 0.3, 1, 1.6, and 2 \(\mu\)g/L is
associatied with chlorophyll \emph{a} concentration thresholds of 20.88,
69.6, 84.24, and 97.49, respectively. When managing for these various
microcystin levels, exceeding these reported chlorophyll \emph{a}
concentrations should be a trigger for further testing and possible
management action.

@@

Over the last decade, numerous events and legislative activities have
raised the public awareness of harmful algal blooms (Rinta-Kanto et al.
2009, HABHRCA 2014, Jetoo et al. 2015). In response the US Environmental
Protection Agency (USEPA) has recently released suggested microcystin-LR
(one of the more common toxins) concentrations that would trigger health
advisories (McElhiney and Lawton 2005, Zurawell et al. 2005, USEPA
2015). Additionally, the World Health Organization (WHO) has proposed
microcystin advisory levels for drinking water and a range of
recreational risk levels (Chorus and Bartram 1999, Organization 2003).
While these levels and associated advisories are likely to help mitigate
the impacts from harmful algal blooms, they are not without
complications.

One of these complications is that they rely on available measurements
of microcystin-LR. While laboratory testing (e.g., chromatography)
remains the gold standard for quantifying microcystin-LR concentrations
in water samples, several field test kits have been developed. Even
though field tests provide a much needed means for rapid assessment,
they are not yet widely used and are moderately expensive (approximately
\$150-\$200 depending on specific kit) with a limited shelf life
(typically one year) (James et al. 2011, Aranda-Rodriguez et al. 2015).
Additionally, each technique requires nuanced understanding of the
detection method (e.g., limit of detection, specific microcystin
variants being measured, and sampling protocol).

@@

We used the 2007 NLA chlorophyll \emph{a} and microcystin-LR
concentration data (USEPA 2009). These data represent a snapshot of
water quality from the summer of 2007 for the conterminous United States
and were collected as part of an ongoing probabilistic monitoring
program (USEPA 2009). Data on chlorophyll \emph{a} and microcystin-LR
concentrations are available for lakes.

@@

Conditional probability analysis provides information about the
probability of observing one event given another event has also occured.
For this analysis, we used CPA to examine how the conditional
probability of exceeding one of the health advisories changes as
chlorophyll \emph{a} increases in a lake. We expect to find higher
chlorohpyll \emph{a} concentrations to be associated with higher
probabilities of exceeding the microcystin-LR health advisory levels. We
also caclulated bootstrapped 95\% confidence intervals (CI) using 1000
bootstrapped samples. Thus, to identify chlorophyll \emph{a}
concentrations of concern we identfiy the value of the upper 95\% CI
across a range of conditional probabilities of exceeding each health
advisory level. As both microcystin-LR and chlorophyll \emph{a} values
were highely skewed right, a log base 10 transformation was used.
Additional details of the specific implementation are available at
\url{https://github.com/USEPA/microcystinchla}. A more detailed
discussion of CPA is beyond the scope of this paper, but see Paul et al.
(2005) and Hollister et al. (2008) for greater detail. Lastly, all
analyses were conducted using R version 3.2.2 and code and data from
this analysis are freely available as an R package at
\href{https://github.com/USAPE/microcystinchla}{\url{https://github.com/USAPE/microcystinchla}}.

@@

In the 2007 NLA, microcystin-LR concentrations ranged from 0.05 to 225
\(\mu\)g/L. Microcystin-LR concentrations of 0.05 \(\mu\)g/L represent
the detection limits. Any value greater than that indicates the presence
of microcystin-LR. Of those lakes with microcystin, the median
concentration was 0.51 and the mean was 3.17. Of all lakes sampled, 21\%
of lakes exceeded the USEPA Child level, 8.8\% of lakes exceeded the
USEPA Adult level,11.7\% of lakes exceeded the WHO Drinking level,and
7.3\% of lakes exceeded the WHO Recreational level. For chlorophyll
\emph{a}, the range was 0.07 to 936 \(\mu\)g/L. All lakes had reported
chlorophyll \emph{a} concentrations that exceeded detection limits. The
median concentration was 7.79 \(\mu\)g/L and the mean was 29.63
\(\mu\)g/L. The associations between chlorophyll \emph{a} and the upper
confidence interval across a range of conditional probability values is
shown in Table \ref{tab:mc_chla_table}. Specific chlorophyll \emph{a}
that are associated with greater than even odds of exceeding the
advisory levels were 0.07, 0.07, 2.89, and 10.27 for 0.3, 1.0, 1.6 and
2.0 \(\mu\)g/L advisory levels, respectively (Table
\ref{tab:mc_chla_table} \& Figure \ref{fig:multi_cp_plot}).

@@

The association between Log10 microcystin-LR and Log10 chlorophyll
\emph{a} shows a wedge pattern (Figure \ref{fig:chla_micro_scatter}).
This indicates that, in general, higher concentrations of microcystin-LR
almost always co-occur with higher concentrations of chlorophyll
\emph{a} yet the inverse is not true. Higher chlorophyll \emph{a} is not
necessarily predictive of higher microcystin-LR concentrations; however,
chlorophyll \emph{a} may be predictive of the probability of exceeding a
certain threshold.

This is the case as the probability of exceeding each of the four tested
health advisory levels increases as a function of chlorophyll \emph{a}
concentration (Figure \ref{fig:multi_cp_plot}). We use this association
to identify chlorophyll \emph{a} concentrations that are associated with
a range of probabilities of exceeding a given health advisory level
(Table \ref{tab:mc_chla_table}). For the purposes of this discussion we
focus on a conditional probability of 50\% or greater (i.e.~greater than
even odds to exceed a health advisory level). The 50\% conditional
probability chlorophyll \emph{a} thresholds represents 30.1\%, 10.6\%,
8.8\%, and 7.9\% of sample lakes for the USEPA Child, the WHO Drinking,
the USEPA Adult, and the WHO recreational levels, respecitvely.

Furthermore, the chlorophyll \emph{a} cutoffs may be used to predict
whether or not a lake exceeds the microcystin-LR health advisories.
Doing so allows us to compare the accuracy of the prediction as well as
evaluate false negatives. Total accuracy of the four cutoffs predicting
microcystin-LR exceedances were 74\% for the USEPA children's advisory,
86\% for the WHO drinking water advisory, 89\% for the USEPA adult
advisory and, 90\% for the WHO regreational advisory (Tables
\ref{tab:child_conmat_table}, \ref{tab:who_drink_conmat_table},
\ref{tab:adult_conmat_table}, \& \ref{tab:who_rec_conmat_table}).
However, total accuracy is only one part of the prediction performace
with which we are concerned.

When using the chlorophyll \emph{a} cutoffs as an indicator of
microcystin-LR exceedances, the error that should be avoided is
predicting that no exceedance has occurred when in fact it has. In other
words, we would like to avoid Type II errors and minimize the proportion
of false negatives. For the four chlorophyll \emph{a} cut-offs we had a
proportion of false negatives of 9\%, 8\%, 6\% and , 5\% for the U.S EPA
childrens drinking water, the WHO drinking water, the USEPA adult
drinking water, and the WHO recreational advisories, respectively. In
each case we miss less than 10\% of the lakes that are in fact exceeding
the microcystin-LR advisory.

@@

A second potential use is to identify past bloom events from historical
data. As harmful algal blooms are made up of many species and have
various mechanisms responsible for adverse impacts (e.g.~toxins,
hypoxia, odors), there is no single definition of a bloom. For cHABs one
approach has been to identify an increase over a baseline concentration
of phycocyanin (Miller et al. 2013). This is a useful approach for
targeted studies, but phycocyanin is also not always available and
measures the predominance of cyanobacterial pigments and not toxins.
Using our chlorophyll \emph{a} cutoffs provides a value that is more
directly associated with microcystin-LR and can be used to classify
lakes, from past surveys, as having bloomed.

Lastly, using chlorophyll \emph{a} is not meant as a replacement for
testing of microcystin-LR or other toxins. It should be used when other,
direct measurements of cyanotoxins are not available. In those cases,
which are likely to be common at least in the near future, using a more
ubiquitous measurement, such as chlorophyll \emph{a} will provide a
reasonable proxy for the probability of exceeding a microcystin-LR
health advisory level and provide better protection against adverse
effects in both drinking and recreational use cases.

@@

\begin{longtable}[c]{@{}rrrrr@{}}
\caption{Chlorophyll \textit{a} concentrations that are associated with
a 50\% probability of exceeding a microcystin-LR health advisory
concentration. \label{tab:mc_chla_table}}\tabularnewline
\toprule
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO
Recreational\tabularnewline
\midrule
\endfirsthead
\toprule
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO
Recreational\tabularnewline
\midrule
\endhead
0.1 & 0.07 & 0.07 & 0.07 & 1.17\tabularnewline
0.2 & 0.07 & 4.38 & 11.84 & 16.80\tabularnewline
0.3 & 2.89 & 17.49 & 32.11 & 45.22\tabularnewline
0.4 & 10.27 & 38.30 & 66.96 & 76.80\tabularnewline
0.5 & 20.88 & 69.60 & 84.24 & 97.49\tabularnewline
0.6 & 38.20 & 100.51 & 114.62 & 125.40\tabularnewline
0.7 & 65.60 & 128.74 & 871.20 & 871.20\tabularnewline
0.8 & 114.62 & 271.44 & 871.20 & 871.20\tabularnewline
0.9 & 166.63 & 338.40 & 871.20 & 871.20\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the USEPA
childrens drinking water advisory.
\label{tab:child_conmat_table}}\tabularnewline
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endfirsthead
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endhead
FALSE & 632 & 90\tabularnewline
TRUE & 179 & 127\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the WHO
drinking water advisory.
\label{tab:who_drink_conmat_table}}\tabularnewline
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endfirsthead
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endhead
FALSE & 844 & 80\tabularnewline
TRUE & 63 & 41\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the USEPA adult
drinking water advisory. \label{tab:adult_conmat_table}}\tabularnewline
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endfirsthead
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endhead
FALSE & 885 & 57\tabularnewline
TRUE & 52 & 34\tabularnewline
\bottomrule
\end{longtable}

@@

\begin{longtable}[c]{@{}lrr@{}}
\caption{Confusion matrix comparing chlorophyll \textit{a} predicted
exceedences (rows) versus real exceedances (columns) for the WHO
recreational water advisory.
\label{tab:who_rec_conmat_table}}\tabularnewline
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endfirsthead
\toprule
& FALSE & TRUE\tabularnewline
\midrule
\endhead
FALSE & 903 & 48\tabularnewline
TRUE & 50 & 27\tabularnewline
\bottomrule
\end{longtable}
